Optimizing Path ORAM for Cloud Storage Applications

### 2014-11-30 paper/paper.tex
Update paper.tex

For all experiments, the parameters were kept at constant values (unless we were testing that parameter). The ORAM tree size (if auto resizing is off) was dependent on the amount of data written to it, twice the total file size. Segment size was 64 KB (optimal as indicated by Figure \ref{fig:segsize}) with bucket sizes of $Z$ = 3.  The maximum stash size was 100. The utilization ratio that triggers tree growth was 0.45 and for tree shrinkage 0.55. We use throughput in Mega Byte per second as the performance metric.
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{510.pdf}
\caption{File Distribution Function showing the cumulative percentage of files of various sizes (KB).}
\label{fig:distfun}
\end{center}
\end{figure}

@@

\subsection{Initial ORAM Efficiency}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash}p{#1}}
\begin{table}
\begin{center}
  \begin{tabular}{| C{1.5cm} | C{3cm} | C{2.5cm} |}
  \hline
  \bf{Disk} & \bf{Disk + Encryption} & \bf{Disk + ORAM} \\
  \hline
  42.13 & 24.42 & 0.66 \\
  \hline
\end{tabular}
\vspace{6pt}
\caption{Throughput (in MB/s) of Path ORAM (before our optimization) and comparisons to two baselines.}
\label{tab:baseline}
\end{center}
\end{table}

@@

\subsection{Dynamic Growing and Shrinking}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{560.pdf}
\caption{Tree resizing demonstration charting size of tree over time.}
\label{fig:resizing}
\end{center}
\end{figure}

>>>>

For all experiments, the parameters were kept at constant values (unless we were testing that parameter). 
The ORAM tree size (if auto resizing is off) was dependent on the amount of data written to it, twice the total file size. 
Segment size was 64 KB (optimal as indicated by Figure \ref{fig:segsize}) with bucket sizes of $Z$ = 3.  
The maximum stash size was 100. 
The utilization ratio that triggers tree growth was 0.45 and for tree shrinkage 0.55. 
We use throughput in Mega Byte per second (MB/sec) as the performance metric.

\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{510.pdf}
\caption{File Distribution Function showing the cumulative percentage of files of various sizes (KB).}
\label{fig:distfun}
\end{center}
\end{figure}

@@

\subsection{Initial ORAM Efficiency}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash}p{#1}}
\begin{table}
\begin{center}
  \begin{tabular}{| C{1.5cm} | C{3cm} | C{2.5cm} |}
  \hline
  \bf{Disk} & \bf{Disk + Encryption} & \bf{Disk + ORAM} \\
  \hline
  42.13 & 24.42 & 0.66 \\
  \hline
\end{tabular}
\vspace{6pt}
\caption{Throughput (in MB/sec) of Path ORAM (before our optimization) and comparisons to two baselines.}
\label{tab:baseline}
\end{center}
\end{table}

@@

\subsection{Dynamic Growing and Shrinking}
\begin{figure}
\begin{center}
\noindent\includegraphics[width=8.5cm]{560.pdf}
\caption{Tree resizing demonstration charting the number of ``real blocks'' stored in the tree and the size of tree over time.}
\label{fig:resizing}
\end{center}
\end{figure}
